### 2013-03-31 exam6/2.tex
a first draft of the section/outline problem

Outline problem

@@

>>>>

\begin{problem} \pts{20}
\noindent
Tobin-Hochstadt needs to automatically manage papers to make it
easier to review them.  He wants to represent a paper in the following
way:

A \emph{Section} has a title and a list of subsections, which are just
sections themselves.  A paper is therefore just a big section.  Here
is an example of a paper (and, of course, an example of a section):

\begin{verbatim}
   Fundies 2, Day 1
   1. OO = struct + fun
   1.1. Rocket
   1.2. Moon
   2. Design
   2.1. Announce
   2.1.1. Assign
   3. End
\end{verbatim}
Note that the section numbers are \emph{NOT} part of the document!

\bigskip
%\vskip{2}

\begin{enumerate}

\item Develop data, class, and interface defintions for sections.

\newpage

\noindent
\item Extend your defininition of \texttt{Section} to support an
\texttt{accept} method that take \texttt{SectionVisitor}s over to
compute over sections.  You will need to define the
\texttt{SectionVisitor} interface.  You may need to define additional
visitors as well, depending on your original data definition.

\newpage

\noindent
\item Write a \texttt{SectionVisitor} that produces the ``outline'' of a section, with the
section numbers.  The result should be an \texttt{ArrayList} of
\texttt{String}s, as seen in the initial example for this problem.

@@

\noindent
\item Here is a defintion for the \texttt{equals} and \texttt{hashCode}
methods for \texttt{Section}s:

\begin{verbatim}
Boolean sameSec(Section s) { ...}

boolean equals(Object o) {
    if (o instanceof Section)
        return this.sameSec((Section)o);
    else
        return false;
}

int hashCode() { return 42; }
\end{verbatim}

\noindent
Develop the \texttt{sameSec} method, which \texttt{equals} relies on.

\noindent
\item The definition for \texttt{hashCode} that we have presented is very
simple, but it will reduce the performance of hash tables of
\texttt{Section}s.  Develop a better version of the \texttt{hashCode}
method.  Make sure that it can distinguish (some) \texttt{Section}s
with the same title but different contents, as well as (some)
\texttt{Section}s with different titles but the same contents.

\ifrubric
\else
\newpage
[Here is some more space for the previous problem.]
\fi
\newpage
\newpage
\end{enumerate}
\end{problem}
